\thesistitle

### 2019-07-30 sections/research.tex
Gap formula

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
public void doStuff(){
|\highlightYellow|  doA(); // Clone instance of
|\highlightYellow|  doB(); // two statements
  doC(); // Gap of one statement
|\highlightBlue|  doD(); // Clone instance of
|\highlightBlue|  doE(); // two statements
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
public void doStuff(){
|\highlightYellow|  doA(); // Clone instance of
|\highlightYellow|  doB(); // two statements
  doF(); // Gap of one statement
|\highlightBlue|  doD(); // Clone instance of
|\highlightBlue|  doE(); // two statements
}
\end{javacode}}
\end{parcolumns}
\caption{Gapped clones.}
\label{fig:gappedclones}
\end{figure}

Apart from this threshold, the gap in between clones may not span over different blocks. Look at figure \ref{fig:type3invalid} for an example of this. We cannot refactor both statements into a single conditional block. We could however use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.

>>>>

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{1-1}$}|
|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{1-2}$}|
\end{javacode}}
\colchunk[2]{
\begin{javacode}
|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{2-1}$}|
a *= 5; // |\textcolor{pgreen}{$N_{2-2}$}|
|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{2-3}$}|
\end{javacode}}
\end{parcolumns}
\caption{Gapped clones.}
\label{fig:gappedclones}
\end{figure}

When applying this formula with the example given in figure \ref{fig:gappedclones}, we get a gap size of 50\%:

\begin{equation}\label{eq:type3r}
\text{T3R Gap Size}=\frac{|\{N_{2-2}\}|}{|\{N_{2-1}\}| + |\{N_{2-3}\}|}*100 = \frac{1}{2}*100 = 50\%
\end{equation}

\subsubsection{The gap may not span a partial block}
Apart from this threshold, the gap in between clones may not span over different blocks. Look at figure \ref{fig:type3invalid} for an example of this. We cannot refactor both statements into a single conditional block. We could however use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
